---
title: "ThreadScheduler"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Code for ThreadScheduling Probability

There are Two Processcor cores each capable of running 2 threads.
A stress test is required to be  performed in the design on a FPGA platform. A selection of tests are picked at random from a pool of tests. 

The expectation was that the tests would run without any hitch over a number of iterations or tries, the hypothesis being that the probability of occurance of  3 slave mode tests scheduled without a corresponding master is very slim.

In reality, it was otherwise

This R program plots the probability of the test Success abd Test Fail over given number of tries and proves that it does not take many tries to end up with a failure

```{r, message = FALSE}
#This program attempts to get the plot of sucessful runs over number of tries
library(dplyr)
library(RSQLite)
library(tidyr)
library(ggplot2)
library(readr)
library(stringr)
library(scales)
library(mixtools)


```
## Details
Here is how the test is set up 

* There are 4  tests  A, B, C, and D
    + Further more, test A can run in Master or slave modes - M or S
* There are 2 cores with two threads each
* Each thread is named t~0~, t~1~, t~2~ and t~3~
* 4 instances of each test is picked at random and scheduled 
* 4 instances of each of the tests, A,B, C and D  create a pool of 16 tests to choose from 
* For all practical purposes, the total pool of tests can be thought of as
    + MSSS
    + BBBB
    + CCCC
    + DDDD
 
* There are 4 threads to schedule from this pool of tests

* Only if M is scheduled in t~0~, S can run sucessfully
    + e.g MSSS runs successfully -> q3

        - MSSX runs successfully
        - MSXS runs successfully ->q2
        - MXSS runs successfully

        - MSXX runs successfully
        - MXSX runs successfully ->q1
        - MXXS runs successfully

        - MXXX runs successfully ->q0

        - XXXX runs successfully ->qx
# Probability 
* Example
    + A in slave  mode (S) can be picked  picked with a probability of 4/16 into t~1~
    + A in slave  mode (S) can be picked  picked with a probability of 3/15 into t~2~
    + A in slave  mode (S) can be picked  picked with a probability of 2/14 into t~3~
    + A in Master mode (M) can be picked  picked with a probability of 1/13 into t~0~
    + Let q~3~ be the probability of a successful thread scheduling 

#### Let us set up the Probability of the other cases enumerated above
```{r}
q3 <- (1/13) * (4/16) * (3/15) * (2/14)

q2 <- 3 * (2/13) * (4/16) * (3 /15)* (12/14)

q1 <- 3 * (3/13) * 3 * (4/16) * (12/15) * (11/14)

q0 <- (4/13) * (12/16) * (11/15) * (10/14)

qx <- (12/16) * (11/15) * (10/14) * (9/13)

```
#### total probability of a sucessful run in 1 try 
```{r}
q <- q3 + q2 + q1 + q0 + qx
q
```

#### probability of failure in 1st try

```{r}
 1-q
```
 
#### Probability of failure in  2 trys
```{r}
q * ( 1-q)
```

#### Probability of failure in 3 trys

```{r}
q*q *( 1-q)
```
#### probability of failure in 4096th try 
```{r}
q^4095 * ( 1-q)
```
#### Probability of success in 4096 tries
```{r}
P <- q^4096
P
```
#### Probability of failure in 4096 tries
```{r}
F <- 1-P
F
```


#### Define a function 
```{r}
# gives success probability in xth tries
sched_success <- function (x, q) { q^(x)}

# gives success probability in xth tries
sched_fail    <- function (x, q) { 1 -  (q^(x))}

# create a vector of 
tries <- c(seq(1,20, by = 1))
```
#### print y pass

```{r}
y_pass <- sapply(tries, sched_success,q)
y_pass
```
#### print y fail 

```{r}

y_fail <- sapply(tries, sched_fail,q)
y_fail

```

# Plot
```{r, echo = FALSE}
# Data Layer
n <-(ggplot)

# Data + Aesthetics Mapping 
n <-ggplot(data_frame(tries),aes(x= tries, y = sapply(tries, sched_success,q)))

# Data + aes + Geometries 
n <- n + geom_jitter(aes( color = "success")) 

n <- n + geom_jitter(aes( x = tries, y = sapply(tries, sched_fail,q),color = "fail"))

# Data + Aesthetic Mapping +  Geom + Facets
#n <- n + facet_grid(. ~ Department.Title ) 

#Data + Aesthetics + Geoms + Facets + Statistics
# ... add a linear regression model here

#Data + Aesthetics + Geoms + Facets + Statistics + Co-ordinates
#n <- n + scale_y_discrete(limits=c("00000","120000"), breaks=seq(00000,120000,10000))
n <- n + xlab("Number of tries")
n <- n + ylab("Probability of Success or Failure ")

#Data + Aesthetics + Geoms + Facets + Statistics + Co-ordinates + Theme 
#n <- n + theme(axis.text.x = element_text(angle=305))

print(n)


```

 
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
